The Werewolf Among Us: Humans vs LLMs in Multi-Agent Games

### 2025-04-23 Quarto/paper.qmd
Final EDA

---
title: Modeling Persuasion Behaviors in Social Deduction Games
author:
  - name: First Author
    orcid: 0000-0000-0000-0000
    corresponding: true
    email: first.author@university.edu
    roles:
      - Investigation
      - Methodology
      - Software
      - Writing – original draft
      - Visualization
    affiliations:
      - Department of Computer Science, University Name
  - name: Second Author
    orcid: 0000-0000-0000-0000
    corresponding: false
    email: second.author@university.edu
    roles:
      - Conceptualization
      - Data Curation
      - Writing – review & editing
      - Project administration
    affiliations:
      - Department of Computer Science, University Name
keywords:
  - social deduction games
  - persuasion modeling
  - Werewolf Among Us dataset
  - large language models
  - multimodal analysis
abstract: |
  This final project for CSCI‑5423 explores the modeling of persuasion behaviors in the text-based social deduction game Werewolf. We leverage the multimodal “Werewolf Among Us” dataset (Lai, 2022) and evaluate several large language models on their ability to persuade, deceive, and cooperate within game dialogues. Through a combination of feature engineering, sequence modeling, and reinforcement learning agents, we compare performance against baseline classifiers and analyze key linguistic strategies.
date: last-modified
citation:
  container-title: CSCI‑5423 Final Report
---

>>>>

---
title: "The Werewolf Among Us: Humans vs LLMs in Multi-Agent Games"
author:
  - name: Bhavana Jonnalagadda
    orcid: 0009-0009-1054-0995
    corresponding: true
    email: bhavana.jonnalagadda@colorado.edu
    affiliations:
      - name: University of Colorado Boulder
        id: 1
        city: Boulder
        state: CO
  - name: Riley Jones
    email: rjones@colorado.edu
    affiliations:
      - id: 1
keywords:
  - social deduction games
  - persuasion modeling
  - Werewolf Among Us dataset
  - large language models
  - multimodal analysis
abstract: |
  This final project for CSCI‑5423 explores the modeling of persuasion behaviors in the text-based social deduction game Werewolf. We leverage the multimodal “Werewolf Among Us” dataset (Lai, 2022) and evaluate several large language models on their ability to persuade, deceive, and cooperate within game dialogues. Through a combination of feature engineering, sequence modeling, and reinforcement learning agents, we compare performance against baseline classifiers and analyze key linguistic strategies.
date: last-modified
citation:
  container-title: CSCI‑5423 Final Report
---
